\documentclass[10pt]{article}
\usepackage{fullpage}
\usepackage{amsmath,amsfonts,amsthm}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{hhline}

\graphicspath{{./imgs/} {./imgs/Q1/} {./imgs/Q2/}}

% these are compressed lists to help fit into a 1 page limit
\newenvironment{enumerate*}%
  {\vspace{-2ex} \begin{enumerate} %
     \setlength{\itemsep}{-1ex} \setlength{\parsep}{0pt}}%
  {\end{enumerate}}
 
\newenvironment{itemize*}%
  {\vspace{-2ex} \begin{itemize} %
     \setlength{\itemsep}{-1ex} \setlength{\parsep}{0pt}}%
  {\end{itemize}}
 
\newenvironment{description*}%
  {\vspace{-2ex} \begin{description} %
     \setlength{\itemsep}{-1ex} \setlength{\parsep}{0pt}}%
  {\end{description}}

\DeclareMathOperator*{\E}{\mathbb{E}}
\let\Pr\relax
\DeclareMathOperator*{\Pr}{\mathbb{P}}

\newcommand{\inprod}[1]{\left\langle #1 \right\rangle}
\newcommand{\eqdef}{\mathbin{\stackrel{\rm def}{=}}}

\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}

\author{Jacob Clouse}
\title{Spring 2023 - ICSI 526\\Homework $2$}

\begin{document}

\maketitle

\section{Running CBC and OFB modes, Calculating the IOC}
\noindent There are two separate AES files included: One contains my code for CBC mode and the other contains my code for OFB mode. I couldn't get them to work together inside of the same file so I had to split them out into different programs. NOTE: This program was mainly coded on a Linux Mint machine using BASH to compile and Git/Github to host my code (using a private git repo).
\vspace{0.2in}
\\
\noindent \textbf{How to Compile and Run CBC Mode: } 
\begin{enumerate}
	\item Make sure you have a working copy of the Java JDK and a text editor on your machine (I use VS Code because of the built in terminal).
	
	\item Make a copy of the \textbf{CBC} folder I have provided and cd into it with your terminal. The ONLY two items you should have inside are the \textbf{AES.java} and \textbf{AES\_Demo.java} files (the demo is required to run this program).
	
	\item You can compile the program by using the syntax: \begin{verbatim} javac AES_Demo.java AES.java \end{verbatim}
	This should create a several class files within the \textbf{CBC} folder, including a \text{AES\_Demo.class} file.
	
	\item Now you can run this file using the syntax: 
	\begin{verbatim} java AES_Demo \end{verbatim} 
	If successful, a window should pop up that will allow you to select your sample data. 
	
	\item 

\end{enumerate}

\vspace{0.2in}
\resizebox{1.0\textwidth}{!}{
\begin{tabular}{|p{1cm}|c|c|}
	\hline
	\multicolumn{1}{|c|}{\textbf{Mode}} & \multicolumn{1}{c|}{\textbf{\% Dup}} & \multicolumn{1}{c|}{\textbf{IOC}} \\
	\hline
	
	\multirow{3}{.75cm}{ECB} 
	& 0\% & 0.01995247623811906 \\
	\cline{2-3}
	& 25\% & 0.024443221610805404 \\
	\cline{2-3}
	& 50\% & 0.03179889944972486 \\
	\hline
	
	\multirow{3}{.75cm}{CBC} 
	& 0\% & 0.003902951475737869 \\
	\cline{2-3}
	& 25\% & 0.003873936968484242 \\
	\cline{2-3}
	& 50\% & 0.003944972486243122 \\
	\hline
	
	\multirow{3}{.75cm}{OFB} 
	& 0\% & 0.00392896448224112 \\
	\cline{2-3}
	& 25\% & 0.003864432216108054 \\
	\cline{2-3}
	& 50\% & 0.003921960980490245 \\
	\hline
\end{tabular}
}


\noindent \textbf{Problem 1} can be efficiently solved by ...


\vspace{1in}







\if false
Theorem~\ref{th:root} is stated below. Its proof follows.

\begin{theorem}
	The square root of $2$ is irrational.
	\label{th:root}
\end{theorem}

\begin{proof}
For the sake of contradiction suppose $\sqrt{2}$ is rational. Write $\sqrt{2} = a/b$ with $a,b$ positive integers with gcd $1$. Then $2 = a^2/b^2$, so $a = 2k$ is even. Then $2 = 4k^2/b^2$ so that $b = 2k^2$, implying $b$ is even. This contradicts that $a,b$ have gcd $1$.
\end{proof}

Some random facts in a list:

\begin{itemize*}
	\item Compared with the ``itemize'' environment in \LaTeX, itemize$^*$ has smaller separation between bullet points.
	\item If $\pi(x)$ is the number of primes less than or equal to $x$, then
$\lim_{x\rightarrow\infty} \frac{\pi(x)}{x/\ln(x)} = 1$.
	\item Here is a numbered equation on a separate line 
	\begin{equation}
		\sum_{\substack{1\le i\le 2n\\i\ \mathrm{even}}} i = \frac{2n(n+1)}2
	\end{equation}
\end{itemize*}
\fi
\end{document}